Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/JFLA2022/paper.tex
add a remark about the number of steps of a battle

 \TODO[Pierre]{Using equations for $H'$ as rewrite rules, we could prove nice minorations: for instance, the number $H'_{\omega^3}(3)$ has at least $2^{10^{21}}$ binary digits.}
\section{Main features}

>>>>

\TODO[Pierre]{
Using the equations for $H'$ as rewrite rules, we could ``compute'' the number of rounds of the battle starting with the hydra of Figure~\ref{fig:start} and $0$ as initial step. this number has
at least $2^{10^{21}}$ binary digits. Obtaining this result is an interesting example of relationship between proof and computation.}

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[very thick, scale=0.3]
  \node (h1) at (4,0){$\bullet$};
  \node (h2) at (2,2){$\bullet$};
  \node (h3) at (0,4){$\bullet$};
  \node (h4) at (1,4){$\bullet$};
  \node (h5) at (2,4){$\bullet$};
  \node (h6) at (4.5,2){$\bullet$};
  \node (h7) at (6.5,2){$\bullet$};
  \node (h8) at (8.5,2){$\bullet$};
    \draw (h1) -- (h2) ;
    \draw (h2) -- (h3) ;
    \draw (h2) -- (h4) ;
    \draw (h2) -- (h5) ;
    \draw (h1) -- (h6) ;
    \draw (h1) -- (h7) ;
    \draw (h1) -- (h8);
 \end{tikzpicture}

  \caption{The hydra corresponding to the ordinal $\omega^3+3$}
  \label{fig:start}
\end{figure}

\section{Main features}
